---
title: 'Final Assignment :: Shiny App'
author: "Partha Hazra"
date: "March 31, 2019"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Purpose and Details

The assignment was built as part of a deliverable for the course Developing Data Products 
as part of the Coursera Data Science Specialization.This peer assessed assignment has two 
parts. 

- A. I need to create a Shiny application and deploy it on Rstudio's servers. 
- B. Second, I shall use Rstudio Presenter to prepare a reproducible pitch 
presentation about the application.

The app developed for the first part of the assignment demo is 
avalilable at https://parthashazrads.shinyapps.io/TruChoiceCar/

Source code for ui.R and server.R files are available on the 
GitHub repo @ https://github.com/parthashazra/Shiny-App-Data-Products---JHU-DSS

## Application Overview

TruChoiceCar site helps user to select correct car for their upcoming trip based on 
various parameter.

User need to provide your trip detail like distance, price of gasoline, maximum allowed 
expenditure for gasoline, etc. 

Based on these user feedback, Shiny App calculates internally and recommends cars based on 
your prefernce criteria ordered by expenditure on gasoline.

The result contains filters selected cars will show in a table on the main content with 
using the mtcars dataset from [R].

## Sneak peek in mtcars Dataset

```{r echo = FALSE,message=FALSE,warning=FALSE}
library(datasets)
library(plotly)


print("First 10 entries from mtcars dataset")
mtcars[1:10,]
```

## Basic Data Exploration

```{r echo = FALSE,message=FALSE,warning=FALSE}
par(mfrow = c(2,2))

plot(mtcars$cyl,mtcars$mpg,xlab = "Number of Cylinder",ylab = "MPG Indicator")
plot(mtcars$hp,mtcars$mpg,xlab = "Horsepower",ylab = "MPG Indicator")
plot(mtcars$wt,mtcars$mpg,xlab = "Weight of the car",ylab = "MPG Indicator")
plot(mtcars$disp,mtcars$mpg,xlab = "Displacement Count",ylab = "MPG Indicator")
```


## Basic Data Exploration

For the sake of time for the reviewer, I have restricted data exploration at basic level. 
We found that MPG is strongly related to number of cyliders, horsepower as well as weight'
of the car. Displacement also impacts MPG negatively.

Further analysis can explore more such interesting information if we use lm or 
regression techniques.

## End of Slide




Thank you for visting my page!!!


